Governing through patronage: the bargain for education in decentralized Brazil

### 2020-10-12 paper/paper.tex
redraft framing

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, basic mathematical operations beyond the reach of most \citep{vegas_raising_2007}. The World Bank refers to as ``learning poverty'': poor learning when access to a schooling already exists.\footnote{For more information, see \hyperlink{here}{https://www.worldbank.org/en/topic/education/brief/learning-poverty}.} As scholarly focus shifts from public service provision \citep{kaufman_globalization_2001, alesina_public_1999} to the quality of services themselves \citep{}

>>>>

Across the world, vulnerable populations rely on governments for access to basic public services such as education. In the developing world, the quality of public education remains low: functional illiteracy is widespread, and basic mathematical operations beyond the reach of many \citep{vegas_raising_2007}. The World Bank refers to this phenomenon as ``learning poverty'': stunted learning when access to a schooling exists.\footnote{For more information, see \hyperlink{here}{https://www.worldbank.org/en/topic/education/brief/learning-poverty}.}

Understanding who benefits from these services and how politicians decide on that allocation is a well-established tradition in political science \citep{boix_democracy_2003, dixit_determinants_1996}. But we have less intuition on services that are de facto open to all: public education.
